Austraits -- a curated plant trait database for the Australian flora

### 2019-04-10 ms.Rmd
Reworking formatting of citations
- now using csl file to generate citations in proper nature style
- at the same time, lots of cleaning in austraits data too (see https://github.com/traitecoevo/austraits/issues/176)

## Assumes to items exist in global name space
if(!exists("austraits")) {
  austraits <- readRDS("data/austraits.rds")
  # stop("austraits must exist in global name space to knit a report")
}

@@

sources_all <- 
  bind_rows(
    austraits$methods %>% select(dataset_id, citation = source_primary_citation) %>% distinct() %>% mutate(type="primary"),
    austraits$methods %>% select(dataset_id, citation = source_secondary_citation) %>% distinct() %>% mutate(type="secondary")
  ) %>% 
  na.omit() %>% 
  arrange(dataset_id)

sources_unique <- tibble(citation=unique(sources_all$citation)) %>% mutate(source_number=1:n())

sources_all <- sources_all %>% left_join(sources_unique, by = "citation")

refs <- sources_all %>% group_by(dataset_id) %>% 
  summarise(refs = paste(sort(source_number), collapse = ", "))

@@

trait_categories <- read_csv("data/trait_categories.csv")

data_geo <- 
  left_join(by=c("dataset_id", "site_name"),
      select(austraits$traits, -original_name), sites) %>%
  left_join(by="species_name",
      select(austraits$taxonomy, species_name, family)) %>% 
  left_join(refs, by=c("dataset_id"))

n_records <- 
  data_geo %>% 
  group_by(trait_name) %>%
  summarise(
            Description = "",
            Type= "",
            `Records (all)` = n(),
            `Records (geo.)` = sum(!is.na(`longitude (deg)`) & !is.na(`latitude (deg)`)),
            Studies = n_distinct(dataset_id),
            Species = n_distinct(species_name),
            Families = n_distinct(family),
            `Data Citations` = unique(refs) %>% paste(collapse = ", ")
            ) %>% 
  left_join(trait_categories, by=c("trait_name")) %>% 
  select(Tissue = tissue, Category = category, Trait = trait_name, everything()) %>% 
  arrange(Tissue, Category, Trait)

@@

n_records %>%
  kable()
```

@@

```{r, results='asis'}
sprintf("%s. %s", sources_unique$source_number, sources_unique$citation) %>% paste(collapse = "\n\n") %>% writeLines()
```

>>>>

## Assumes to items exist in global name space
austraits <- readRDS("data/austraits.rds")

@@

tmp <- RefManageR::WriteBib(austraits$sources, "references.bib")

sources_all <- 
  bind_rows(
    austraits$methods %>% select(dataset_id, citation = source_primary_key) %>% 
            distinct() %>% mutate(type="primary"),
    austraits$methods %>% select(dataset_id, citation = source_secondary_key) %>% 
            distinct() %>% mutate(type="secondary")
  ) %>% 
  na.omit() %>% 
  arrange(dataset_id) %>% 
  group_by(dataset_id) %>% 
  summarise(refs = sprintf("@%s", citation) %>% 
  paste(collapse = "; "))

@@

trait_categories <- read_csv("data/trait_categories.csv", col_types = cols(.default = "c"))

data_geo <- 
  left_join(by=c("dataset_id", "site_name"),
      select(austraits$traits, -original_name), sites) %>%
  left_join(by="species_name",
      select(austraits$taxonomy, species_name, family)) %>% 
  left_join(sources_all, by=c("dataset_id"))

n_records <- 
  data_geo %>% 
  group_by(trait_name) %>%
  summarise(
            Description = "",
            Type= "",
            `Records (all)` = n(),
            `Records (geo.)` = sum(!is.na(`longitude (deg)`) & !is.na(`latitude (deg)`)),
            Studies = n_distinct(dataset_id),
            Species = n_distinct(species_name),
            Families = n_distinct(family),
            `Data Citations` = refs %>% unique() %>% paste(collapse = "; ")
            ) %>% 
  left_join(trait_categories, by=c("trait_name")) %>% 
  select(Tissue = tissue, Category = category, Trait = trait_name, everything()) %>% 
  arrange(Tissue, Category, Trait)

@@

n_records %>%
  select(-Tissue, Description) %>%
  kable()
```

@@

## Version 1 - via bib.print

```{r, results='asis', eval=TRUE}
sources_unique <-
  bind_rows(
    austraits$methods %>% select(citation = source_primary_citation)  %>% mutate(type="primary"),
    austraits$methods %>% select(dataset_id, citation = source_secondary_citation) %>% mutate(type="secondary")
  ) %>%
  select(citation) %>%
            distinct() %>% 
            mutate(source_number=1:n())

sprintf("%s. %s", sources_unique$source_number, sources_unique$citation) %>% paste(collapse = "\n\n") %>% writeLines()

## Version 3 - via csl

```{r, results='asis', eval=FALSE}

austraits$sources %>% sapply(function(i) i$key) -> keys

sprintf("@%s",keys) %>% paste(collapse = "; ") %>% writeLines()
```
